The ChEMBL database as Linked Open Data

### 2012-03-29 article.tex
Some talk about recent content changes

>>>>

In contrast to earlier releases of ChEMBL-RDF, it now contains the chemical properties
provided by the ChEMBL database as calculated by ACD/Labs and XXXXX. The data includes
chemical properties like polar surface area, pKa and logP, counts for hydrogen bond donor
and acceptor, and rotational bonds. This data is provided for XXXXX structures.

The ChemSpider co-authors complemented the original ChEMBL data with ChemSpider identifiers
for the chemical structures in the data set. Links were generated by ....

Valery: FIXME

Resulting in 1073967 ChemSpider identifiers.
